\mytitile\\~

### 2019-12-27 document.tex
Short lines

% ****** Start of file aipsamp.tex ****m*
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 prx,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

	\begin{abstract}
	In this work, we study a superconducting artificial molecule composed of two magnetic-flux-tunable transmons with intense light while monitoring its state via joint dispersive readout. At certain fluxes, the molecule demonstrates a complex spectrum deviating qualitatively from the solution of the Schrödinger equation without driving. We reproduce the observed extra spectral lines accurately by numerical simulations, and find them to be a consequence of an Autler-Townes-like effect when a single tone is simultaneously dressing the system and probing the transitions between new eigenstates. We present self-consistent analytical models that account for both these processes at the same time and agree well with both experiment and numerical simulation. This study is an important step towards understanding the behaviour of more complex systems of many atoms interacting with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting artificial atoms (SAA) were used in numerous experiments in a compelling demonstration of the validity of fundamental quantum mechanical laws\cite{you2011atomic}. Due to synthetic nature of SAA, their Hamiltonians can be pre-designed and engineered which makes them a particularly versatile tool for studies in quantum optics. Notably, their parameters may be varied in such a wide range that novel physical effects previously inaccessible for natural systems may be directly observed.

One of the most prominent milestones, that superconducting quantum circuits have attained just in a few years after their first demonstration, is the strong coupling with light in {circuit QED}\cite{wallraff2004strong, chiorescu2004coherent} meaning that the decoherence rates are smaller than the Rabi frequency. Currently, they are surpassing all other implementations of strong coupling in terms of coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and molecules, SAA do not even require confined radiation to implement strong coupling with light: they may be coupled unprecedently strongly to the free-propagating electromagnetic waves in 1D on-chip waveguides\cite{astafiev2010resonance} without using cavities at all. The Rabi frequency in this case may reach 50\% of the transition frequency\cite{deng2015observation} which is even beyond strong coupling regime\cite{forn2019ultrastrong}. To correctly describe the behaviour of an atom in these conditions, the so-called \textit{dressed atom approach}\cite{cohen1998atom} is employed when the radiation has to be directly included in the Hamiltonian and affects its level structure.

So far, the main experiments in on-chip quantum optics with intense propagating light were focused on single artificial atoms\cite{baur2009measurement, sillanpaa2009autler, astafiev2010resonance, novikov2013autler, suri2013observation, koshino2013observation, braumuller2015multiphoton, peng2018vacuum, gasparinetti2019two}. In all these works, light dressing of the atom manifests itself through Mollow triplets or Autler-Townes splittings of different kinds. However, despite the recent successes in control of large arrays of interacting SAA\cite{Song574, ye2019propagation, arute2019quantum}, there were, up to our best knowledge, no experiments concerning interaction of such composite structures with intense propagating light. While studies has been done concerning dressing multi-atomic systems in a cavity\cite{fink2009dressed, macha2014implementation, shulga2017observation, yang2018probing}, their interaction with intense free radiation is also attractive since light frequency may be easily tuned to observe various absorption processes for arbitrary configurations of the system's parameters.

In this work, we study an system of two strongly coupled artificial atoms: a superconducting artificial molecule\cite{kou2017fluxonium} (SAM). We use two Xmon-type\cite{barends2013coherent} transmons\cite{koch2007charge} interacting with each other through a cavity bus\cite{majer2007coupling}. Microwave radiation is applied to this system through an on-chip coplanar waveguide while its state can be monitored by dispersive readout using the same coupling cavity\cite{chow2010detecting}. We find that strong interaction of the SAM with microwaves calls forth multiphoton transitions and Autler-Townes-like effects that could only be explained in the dressed picture. We note that although the A-T splittings have been investigated before in a wide range of quantum systems (including natural molecules\cite{tamarat1995pump, ahmed2012autler}), we find some qualitatively new spectral manifestations of the dressing effect. One of the reasons for this is that the natural molecules which could in principle demonstrate such effects do not have enough controllability and coherence. Alternatively, previous studies with SAA have either involved just a single atom or have demonstrated only the standard spectral signatures known from the quantum optics (see Appendix \ref{sec:3-level-at}).

Remarkably, besides its fundamental importance, this experiment may be useful for future quantum computers: a quantum engineer should account for the observed behaviours carefully controlling the driving power (for instance, as we will show, the bSWAP gate\cite{poletto2012entanglement} is directly affected).

The manuscript consists of four main parts and an Appendix. Section I is this introduction; Section II is devoted to the approaches that were used in our study; Section III contains the results of our experimental and theoretical research, including extensive numerical simulations and analytical analysis; finally, in Section IV we make a conclusion of our work and discuss future prospects. The Appendix contains important details of the theoretical framework that we use.

@@

\subsection{Device design and fabrication}
We have designed the SAM as a pair of transmon (Xmon) SAAs with asymmetric SQUIDs\cite{hutchings2017tunable} ($E^1_{J, \sum}/2\pi = 24.3$ GHz, $E^2_{J,\sum}/2\pi = 18.3$ GHz, $E^{1,2}_C = 220$ MHz, $d^{1,2} =0.75$) coupled to a single notch-type\cite{probst2015efficient} $\lambda/4$ resonator ($\omega_r/2\pi \equiv f_r = 7$ GHz, $\kappa = 1/100\ \text{ns}^{-1}$) which both couples\cite{majer2007coupling} the transmons and allows the joint\cite{chow2010detecting} readout o	f their states. In \autoref{fig:experiment}~(a), the optical photograph of the device is shown depicting the layout of the components. The resonator in its upper part is connected to a coplanar waveguide through which the readout is performed. In its lower part, it is coupled to the transmons by a dual ``claw''\cite{barends2013coherent} coupler. Flux lines that allow independent control of the transmon frequencies are coming from the sides. Finally, the excitation waveguide coming from below directs microwave signal towards the SAM. In \autoref{fig:experiment}~(b) the equivalent electrical circuit of the device. The resonator fundamental mode is approximated as an LC-circuit (in the middle), the transmons are shown in colour on the sides as the LC-circuits as well, but with tunable non-linear inductances. A capacitively coupled excitation line is also shown in green. Finally, in \autoref{fig:experiment}~(c) we show schematically the frequencies of the transmons depending on the external magnetic flux. Since an effective junction of the first transmon is larger, its spectrum (orange) lies higher in frequency the spectrum of the second transmon (blue). Using both coils, it is possible to align them so that the lower sweet-spot of the orange transmon is just below the upper sweet-spot of the blue transmon (see the dashed rectangle,  \autoref{fig:experiment}~(c)). This configuration is chosen as it is possible to track higher energy level intersections through multi-photon transitions using a single spectroscopic scan since the transmons are close to each other in frequency. Additionally, the transmons are better protected from the flux noise in this area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical photograph of the device (false coloured). Two transmons (orange, 1 and blue, 2) are coupled capacitively to a $\lambda/4$ coplanar resonator. Frequency control lines come from both sides, and from below a microwave excitation waveguide is connected (green). \textbf{(b)} The equivalent electrical circuit. Tunable Josephson junctions are SQUIDs with magnetic flux control. \textbf{(c)} Frequencies of the $ge$ transitions of the transmons $\omega_1(\Phi_e)$ and $\omega_2(\Phi_e)$ depending on the external magnetic flux (proportional to the currents applied to control lines). In this work, we focus on the area inside the dashed rectangle.}
	\label{fig:experiment}
\end{figure}

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & -220 & -220 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only different in the frequency tuning range and coherence times measured in the lower sweet spot for the 1\textsuperscript{st} one and in the higher sweet spot for the 2\textsuperscript{nd}. The coupling strength $J$ depends on the transmon frequencies and is specified here for $\omega_1 = \omega_2 = 5.32$ GHz.}
	\label{tab:parameters}
\end{table}

@@

A single transmon SAA can be considered as an oscillator with a quartic perturbation describing the leading-order anharmonicity. Therefore, in the main text we avoid using the standard charge and phase operators and write down its Hamiltonian using the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat b^{\dagger}\hat b +\frac{1}{2}\alpha \hat b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\end{equation}
where $\omega$ is its $\ket{0}\rightarrow\ket{1}$ (or from ground to first excited state, $ge$) transition frequency and $\alpha$ is the anharmonicity of the transmon. Additionally, by applying external magnetic flux $\Phi_e$ (via a control current) it is possible to control $\omega = \omega(\Phi_e)$\cite{koch2007charge}. In our modelling, we take into account only the three lowest states of the transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

To drive a quantum system, one should irradiate it by a monochromatic microwave signal of frequency $\omega_d$ using a capacitively coupled transmission line. The driving term between the transmon and the field is then modelled by the following operator: 
\begin{equation}
\hat H_{d} = \hbar \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
\end{equation}
where $\Omega$ is the driving amplitude coinciding with the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.

Now, the complete Hamiltonian of SAM contains two terms describing each of them (with the corresponding annihilation operators $\hat b$ and $\hat c$, the $ge$ frequencies $\omega_{1,2}$ and anharmonicities $\alpha_{1,2}$), two terms representing the interaction of each transmon with the driving field at the same frequency $\omega_d$, and the transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat b^\dag)(\hat c+\hat c^{\dagger})$ is the transverse interaction between the atoms. Strictly speaking, $J = J(\omega_1, \omega_2)$ depends on the transmon frequencies\cite{koch2007charge}, but we take $J$ to be a constant as in \autoref{tab:parameters} due to its negligible variation for our range of frequencies.

For brevity, the SAM Hamiltonian without driving terms and the corresponding eigenenergies will be denoted below as ``unperturbed''.

@@

Besides the unitary evolution, we take into account the incoherent processes of relaxation and dephasing for each transmon. They are modelled using the Lindblad equation with the following collapse operators\cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, \hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, \hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual relaxation rates, and $\gamma_{\phi (1,2)}$ are the pure dephasing rates. As one can see, the collapse operators are in a separable form, i.e. acting only upon a single transmon each. This is a valid approach until the coupling strength $J$ is not too large\cite{beaudoin2011dissipation}. Therefore, the complete evolution equation for the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho = \frac{i}{\hbar}[\hat \rho, \hat H] + \sum_{\alpha, i} \mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho = \mathcal{L}\hat\rho, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = \hat{{O}} \hat \rho \hat{{O}}^\dag - \frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat \rho\}$ and $\mathcal{L}$ is the Liouville superoperator or the Liouvillian.

The readout resonator is not included in the model since in the dispersive regime it does not affect the dynamics of the SAM. Hence, the readout is modelled just by using the measurement operator $\hat M(f_p)$ that can be obtained by measuring the transmission $S_{21}(f_p)$ ($f_p$ is the probe frequency near the resonance) through the sample for the nine different states of the SAM $\ket{ij},\ i=0..2,\ j=0..2$\cite{filipp2009two}. Another way to find $\hat M(f_p)$ is to calculate the transmission by offsetting the experimental resonance curve using the dispersive shifts corresponding to these states. Since we have not directly measured the dispersive shifts, in our modelling they are treated as fitting parameters. Finally, the observable value for any state $\hat \rho$ is calculated as $S_{21}^{sim}(f_p) = \Tr[\hat M(f_p) \hat \rho]$.

@@

Numerical simulations are crucial for studying \autoref{eq:master} since is does not allow  analytical solution. Therefore, we have been using the \textit{qutip}\cite{johansson2013qutip} (quantum optics toolbox) to simulate the dynamics and find the steady state of the system for various parameter combinations of the Liouvillian.

Two distinct modes of simulation were used during the modelling. The first one is for the Liouvillians that do not explicitly depend on time (stationary case). In this case, the steady state $\hat \rho_{ss}$ of the system should be calculated from the set of linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} \hat \rho = 0
\end{equation}
This equation is solved with the qutip's \textit{steadystate} function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}. This method is applicable when the driving of the two transmons is at the same frequency since from \autoref{eq:RWA} follows that $\hat H_{int}$ becomes time independent when $\omega_d^1 = \omega_d^2$.

The second mode is required when it is not possible to avoid the time-dependence of the Liouvillian or if one wants to solve the master equation in the laboratory frame. For example, when the transmons have to be excited at different frequencies ($\omega_d^1 - \omega_d^2 = \delta \neq 0$), from \autoref{eq:RWA} we find that even in the doubly-rotating frame, $\hat H_{int}$ is oscillating, and it is not possible to simply drop this term in RWA because it is inherent for the SAM. In this case, to find the steady state of the system one can employ the qutip's \textit{propagator} and \textit{propagator\_steadystate} functions. The propagator is a completely positive map $\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow \hat \rho(t_1)$ describing the time evolution of the system density matrix; for \autoref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering superoperator. Since the Liouvillian is periodic with a period of $T = 2\pi/\delta$, it is possible to calculate the steady state as the eigenvector $\hat \rho_{ss}$ of the single-period propagator $\Lambda(T, 0)$ corresponding to its largest eigenvalue\cite{dittrich1998quantum, rivas2012open}. Upon infinite applications of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]

>>>>

% ****** Start of file aipsamp.tex ****m*
%
%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
%   Version 4.1 of REVTeX, October 2009
%
%   Copyright (c) 2009 American Institute of Physics.
%
%   See the AIP README file for restrictions and more information.
%
% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
% as well as the rest of the prerequisites for REVTeX 4.1
% 
% It also requires running BibTeX. The commands are as follows:
%
%  1)  latex  aipsamp
%  2)  bibtex aipsamp
%  3)  latex  aipsamp
%  4)  latex  aipsamp
%
% Use this file as a source of example code for your aip document.
% Use the file aiptemplate.tex as a template for your document.
\documentclass[%
 pra,
% jmp,
% bmf,
% sd,
% rsi,
 amsmath,amssymb,
%preprint,%
 reprint,%
%author-year,%
%author-numerical,%
% Conference Proceedings
]{revtex4-1}

@@

	\begin{abstract}
	In this work, we irradiate a superconducting 
	artificial molecule composed of two 
	magnetic-flux-tunable transmons with 
	microwave light while monitoring its state 
	via joint dispersive readout. At certain 
	fluxes, the molecule demonstrates a complex 
	spectrum deviating qualitatively from the 
	solution of the Schrödinger equation without 
	driving. We reproduce the observed extra 
	spectral lines accurately by numerical 
	simulations, and find them to be a 
	consequence of an Autler-Townes-like effect 
	when a single tone is simultaneously dressing 
	the system and probing the transitions 
	between new eigenstates. We present 
	self-consistent analytical models accounting 
	both these processes at the same time that 
	agree well with both experiment and numerical 
	simulation. This study is an important step 
	towards understanding the behaviour of more 
	complex systems of many atoms interacting 
	with strong radiation.
	\end{abstract}

@@

Over the past twenty years, superconducting 
artificial atoms (SAAs) were used in numerous 
experiments in a compelling demonstration of the 
validity of fundamental quantum mechanical 
laws\cite{you2011atomic}. Due to synthetic nature 
of SAAs, their Hamiltonians can be pre-designed 
and engineered which makes them a particularly 
versatile tool for studies in quantum optics. 
Notably, high controllability of their parameters 
allows direct observation of novel physical 
effects previously inaccessible for natural 
systems.

One of the most prominent milestones that 
superconducting quantum circuits have reached so 
far is the strong coupling with light in {circuit 
QED}\cite{wallraff2004strong, 
chiorescu2004coherent} when the decoherence rates 
appear smaller than the Rabi frequency. 
Currently, they are surpassing all other 
implementations of strong coupling in terms of 
coherence\cite{forn2019ultrastrong}. 
However, in sharp contrast with natural atoms and 
molecules, SAAs do not even require confined 
radiation to implement strong coupling with 
light: they may be coupled unprecedently strongly 
to free-propagating electromagnetic waves in 1D 
on-chip waveguides\cite{astafiev2010resonance} 
without using cavities at all. The Rabi frequency 
in this case may reach 50\% of the transition 
frequency\cite{deng2015observation} which is even 
beyond strong coupling 
regime\cite{forn2019ultrastrong}. To correctly 
describe the behaviour of an atom in these 
conditions, the so-called \textit{dressed atom 
approach}\cite{cohen1998atom} is employed when 
the radiation has to be directly included in the 
Hamiltonian and affects its level structure.

So far, main experiments in on-chip quantum 
optics with intense propagating light were 
focused on single artificial 
atoms\cite{baur2009measurement, 
sillanpaa2009autler, astafiev2010resonance, 
novikov2013autler, suri2013observation, 
koshino2013observation, 
braumuller2015multiphoton, peng2018vacuum, 
gasparinetti2019two}. In all these works, light 
dressing of the atom manifests itself through 
Mollow triplets or Autler-Townes splittings of 
different kinds. However, despite the recent 
successes in control of large arrays of 
interacting SAAs\cite{Song574, ye2019propagation, 
arute2019quantum}, there were, up to our best 
knowledge, no experiments concerning interaction 
of such composite structures with intense free 
radiation. While there were studies on dressing 
of multi-atomic systems in a 
cavity\cite{fink2009dressed, 
macha2014implementation, shulga2017observation, 
yang2018probing}, their interaction with free 
radiation is no less attractive since its 
frequency may be easily tuned to observe various 
absorption processes for arbitrary configurations 
of the system parameters.

In this work, we study a pair of strongly coupled 
artificial atoms: a superconducting artificial 
molecule\cite{kou2017fluxonium} (SAM). We use two 
Xmon-type\cite{barends2013coherent} 
transmons\cite{koch2007charge} interacting with 
each other through a cavity 
bus\cite{majer2007coupling}. Microwave radiation 
is applied to this system through an on-chip 
coplanar waveguide while its state can be 
monitored by joint dispersive readout using the 
same coupling cavity\cite{chow2010detecting}. We 
find that strong interaction with microwaves not 
only calls forth multiphoton transitions of 
various orders between SAM states, but also 
significantly modifies its level structure. Even 
in a simple diatomic molecule, this leads to 
complex Autler-Townes-like effects involving 
single- and multiphoton  transitions that can 
only be explained in the dressed picture. We note 
that although the A-T splittings have been 
investigated before in a wide range of quantum 
systems (including natural 
molecules\cite{tamarat1995pump, 
ahmed2012autler}), we find qualitatively new 
spectral manifestations of light dressing when 
SAAs are irradiated unequally. We note that there 
were no such experiments with natural molecules, 
which could in principle demonstrate same 
effects, because they lack controllability and 
coherence of superconducting quantum devices, and 
previous studies of SAAs and free radiation have 
either involved just a single atom or have 
demonstrated only the standard spectral 
signatures known from the quantum optics (see 
Appendix \ref{sec:3-level-at}).

Besides its fundamental importance, this 
experiment may be useful for future quantum 
computers: a quantum engineer should account for 
the observed behaviours carefully controlling the 
driving power (for instance, as we will show, the 
bSWAP gate\cite{poletto2012entanglement} is 
directly affected by light dressing).

The manuscript consists of four main parts and an 
Appendix. Section I is this introduction; Section 
II is devoted to the approaches that were used in 
our study; Section III contains the results of 
our experimental and theoretical research, 
including numerical simulations and analytical 
analysis; finally, in Section IV we make a 
conclusion of our work and discuss future 
prospects. The Appendix contains important 
details of the theoretical framework that we use.

@@

\subsection{Device design and control}
We have designed the SAM as a pair of transmon 
(Xmon) SAAs with asymmetric 
SQUIDs\cite{hutchings2017tunable} ($E^1_{J, 
\sum}/h = 24.3$ GHz, $E^2_{J,\sum}/h = 18.3$ GHz, 
$E^{1,2}_C/h = 220$ MHz, $d^{1,2} =0.75$) coupled 
to a single notch-type\cite{probst2015efficient} 
$\lambda/4$ resonator ($f_r = 7$ GHz, $\kappa = 
1/100\ \text{ns}^{-1}$) which both 
couples\cite{majer2007coupling} the transmons and 
allows joint\cite{chow2010detecting} readout of 
their states. In \autoref{fig:experiment}~(a), 
the optical photograph of the device is shown 
depicting the layout of the components. The 
resonator in its upper part is connected to a 
coplanar waveguide through which the readout is 
performed. In its lower part, it is coupled to 
the transmons by a dual 
``claw''\cite{barends2013coherent} coupler. Flux 
lines that allow independent control of the 
transmon frequencies are coming from the sides. 
Finally, the excitation waveguide coming from 
below directs microwave signal towards the SAM. 
In \autoref{fig:experiment}~(b), the equivalent 
electrical circuit of the device is shown. The 
resonator fundamental mode is approximated as an 
LC-circuit (in the middle), the transmons are 
shown in colour on the sides; their SQUIDs are 
represented as tunable Josephson junctions. A 
capacitively coupled excitation line is also 
shown in green. Finally, in 
\autoref{fig:experiment}~(c) we show 
schematically the frequencies of the transmons 
depending on electric current $I$ which we apply 
to an external coil wound around the sample 
holder. Since the effective junction of the first 
transmon is larger, its spectrum (orange) lies 
higher in frequency than the spectrum of the 
second transmon (blue). Using individual 
flux-control lines, it is possible to align the 
SAAs so that the lower sweet-spot of the orange 
transmon is just below the upper sweet-spot of 
the blue transmon (see the dashed rectangle,  
\autoref{fig:experiment}~(c)). This configuration 
is, as we will show in the following, convenient 
to track the energies of highly excited levels 
via multi-photon transitions in a single 
spectroscopic scan. Additionally, the transmons 
are better protected from the flux noise in this 
area being close to their sweet spots.

\begin{figure}
	 	\includegraphics[width=\linewidth]{experiment_2}
	\caption{\textbf{(a)} Optical photograph of 
	the device (false coloured). Two transmons 
	(orange, 1 and blue, 2) are coupled 
	capacitively to a $\lambda/4$ coplanar 
	resonator. Frequency control lines come from 
	both sides, and from below a waveguide for 
	microwave excitation  is connected (green). 
	\textbf{(b)} The equivalent electrical 
	circuit. Tunable Josephson junctions are 
	SQUIDs with magnetic flux control. 
	\textbf{(c)} Frequencies of the fundamental 
	transitions of the transmons $\omega_1(I)$ 
	and $\omega_2(I)$ depending on the current 
	$I$ in an external coil when correctly 
	aligned by the individual flux control lines. 
	In this work, we focus on the area inside the 
	dashed rectangle.}
	\label{fig:experiment}
\end{figure}

\begin{table}
	\begin{ruledtabular}
	\begin{tabular}{rll}
	Parameter & Transmon 1  & Transmon 2\\\hline
	$\omega/2\pi$ [GHz] & 5.12 - 6.3  & 4 - 5.45\\
	$\alpha/2\pi$ [MHz] & -220 & -220 \\
	$T_1$ [$\mu$s]  & 6.82 &  4.41 \\
	$T_2^*$ [$\mu$s]  & 5.14  &  3.33\\\hline
	$J/2\pi$ [MHz] &\multicolumn{2}{c}{8} 
	\end{tabular}
	\end{ruledtabular}
	\caption{SAM parameters. Transmons are only 
	different in the frequency tuning range and 
	coherence times measured in the lower sweet 
	spot for the 1\textsuperscript{st} one and in 
	the higher sweet spot for the 
	2\textsuperscript{nd}. The coupling strength 
	$J$ depends on the transmon frequencies and 
	is specified here for $\omega_1/2\pi = 
	\omega_2/2\pi = 5.32$ GHz.}
	\label{tab:parameters}
\end{table}

@@

A single transmon SAA can be regarded as an 
oscillator with a quartic perturbation describing 
the leading-order anharmonicity. Therefore, in 
the main text we do not use the charge and phase 
operators and write down its Hamiltonian using 
only the annihilation operator $\hat b$:
\begin{equation}
\hat{{H}}_{tr}/\hbar = \omega \hat 
b^{\dagger}\hat b +\frac{1}{2}\alpha \hat 
b^{\dagger}\hat b(\hat b^{\dagger}\hat b-1),
\label{eq:h1tr}
\end{equation}
where $\omega$ is its 
$\ket{0}\rightarrow\ket{1}$, or fundamental, 
transition frequency and $\alpha$ is the 
anharmonicity of the transmon. By applying 
magnetic flux to the transmon's SQUID (either via 
an individual on-chip line or via an external 
coil) it is possible\cite{koch2007charge} to 
directly  control $\omega$. In our modelling, we 
take into account the three lowest states of the 
transmon ($\ket{0},\ \ket{1}$ and $\ket{2}$).

\autoref{eq:h1tr} describes the SAA without 
interaction with light. To model a monochromatic 
microwave signal of frequency $\omega_d$ applied 
through a capacitively coupled transmission line, 
the following driving term should be included in 
the Hamiltonian:
\begin{equation}
\hat H_{d} = \hbar \Omega (\hat b+\hat b^{\dagger}) \cos\omega_d t,
\end{equation}
where $\Omega$ is the driving amplitude coinciding with the frequency of the Rabi oscillations between $\ket{0}$ and $\ket{1}$.

Next, we assemble the model for two coupled 
transmons with the corresponding annihilation 
operators $\hat b$ and $\hat c$, the fundamental 
frequencies $\omega_{1,2}$ and anharmonicities 
$\alpha_{1,2}$. The corresponding Hamiltonian of 
the SAM contains two terms representing each 
transmon, two terms representing the interaction 
of each transmon with the driving field at the 
same frequency $\omega_d$, and the 
transmon-transmon interaction term:
\begin{equation}\label{Hsystem}
\hat H = \hat H_{tr}^{1}+\hat H_{tr}^{2}+\hat H_{d}^1+\hat H_{d}^2+\hat H_{int},
\end{equation}
where $\hat H_{int} = \hbar J (\hat b +\hat 
b^\dag)(\hat c+\hat c^{\dagger})$ is the 
transverse interaction between the atoms. 
Strictly speaking, $J = J(\omega_1, \omega_2)$ 
depends on the transmon 
frequencies\cite{koch2007charge}, but we take $J$ 
to be a constant as in \autoref{tab:parameters} 
due to its negligible variation for our range of 
frequencies.

For brevity, the SAM Hamiltonian without driving 
terms and the corresponding eigenenergies will be 
referred below as ``unperturbed''. Since we take 
3 levels for each transmon, there will be total 9 
basis states of the SAM $\ket{i}\otimes \ket{j} = 
\ket{ij}$, where $i$ and $j$ show the number of 
excitations in the first transmon, and in the 
second one, respectively.

@@

Besides the unitary evolution, we take into 
account the incoherent processes of relaxation 
and dephasing for each transmon. They are 
modelled using the Lindblad equation with the 
following collapse 
operators\cite{bishop2010circuit}:
\begin{equation}\
\begin{split}
\hat{{O}}_{\gamma, 1} = \sqrt{\gamma_1}\, \hat b,\ 
\hat{{O}}_{\phi, 1} = \sqrt{\gamma_{\phi,1}}\, 
\hat b^\dag \hat b,\\
\hat{{O}}_{\gamma,2} = \sqrt{\gamma_2}\, \hat c,\ 
\hat{{O}}_{\phi,2} = \sqrt{\gamma_{ \phi,2}}\, 
\hat c^\dag \hat c,
\end{split}
\end{equation}
where $\gamma_{1,2}$ are the individual 
relaxation rates, and $\gamma_{\phi (1,2)}$ are 
the pure dephasing rates. As one can see, the 
collapse operators are in a separable form, i.e. 
acting only upon a single transmon each. This is 
a valid approach until the coupling strength $J$ 
is not too large\cite{beaudoin2011dissipation}. 
Therefore, the complete evolution equation for 
the system density matrix $\hat \rho$ is
\begin{equation}
\partial_t \hat \rho_{(R)} = \frac{i}{\hbar}[\hat 
\rho, \hat H_{(R)}] + \sum_{\alpha, i} 
\mathcal{D}[\hat{O}_{\alpha, i}] \hat \rho_{(R)} 
= \mathcal{L}\hat\rho_{(R)}, \label{eq:master}
\end{equation}
where $\mathcal{D}[\hat{{O}}]\hat \rho = 
\hat{{O}} \hat \rho \hat{{O}}^\dag - 
\frac{1}{2}\{ \hat{{O}}^\dag \hat{{O}}, \hat 
\rho\}$ and $\mathcal{L}$ is the Liouville 
superoperator, or the Liouvillian; $_{(R)}$ 
denotes if the Hamiltonian and the corresponding 
solution density matrix are in the rotating frame 
with RWA. In this work, we do not alter the 
dissipator terms when changing the reference 
frame despite that it may not be correct in 
general\cite{shavit2019bridging}.

The readout resonator is not included in the 
model since in the dispersive regime it does not 
affect the dynamics of the SAM. Hence, the 
readout is modelled just by some measurement 
operator $\hat M(f_p)$ that can be obtained by 
finding the transmission $S_{21}(f_p)$ ($f_p$ is 
the probe frequency near the resonance) through 
the sample after preparing various states of the 
SAM. Another way to find $\hat M(f_p)$ is to 
calculate $S_{21}(f_p)$ via offsetting the 
experimental resonance curve measured when the 
SAM is in the ground state by the dispersive 
shifts corresponding to the SAM basis 
states\cite{filipp2009two}. Since we have not 
directly measured these dispersive shifts, in our 
modelling they are treated as fitting parameters. 
Finally, the observable value for any state $\hat 
\rho$ is calculated as $S_{21}^{sim}(f_p) = 
\Tr[\hat M(f_p) \hat \rho]$.

@@

Numerical simulations are necessary for studying 
\autoref{eq:master} since is does not have an 
analytical solution. We have been using the 
\textit{qutip}\cite{johansson2013qutip} (quantum 
optics toolbox in Python) to simulate the 
dynamics and to find the steady state of the 
system for various parameter combinations of the 
Liouvillian.

Two distinct modes of simulation were used in the 
modelling. The first one is for the Liouvillians 
that do not explicitly depend on time. In this 
case, the steady state $\hat \rho_{ss}$ of the 
system should be calculated from the set of 
linear equations obtained from \autoref{eq:master}
\begin{equation}
\partial_t \hat \rho = 0  \Rightarrow \mathcal{L} 
\hat \rho = 0
\label{eq:steady}
\end{equation}
This equation is solved with the qutip's 
\textit{steadystate} 
function\footnote{http://qutip.org/docs/4.0.2/guide/guide-steady.html}.
 This method is applicable when the driving 
frequency for both transmons is the same because 
from \autoref{eq:RWA} follows that $\hat H_{int}$ 
is time independent when $\omega_d^1 = 
\omega_d^2$.

The second mode is required when it is not 
possible to avoid the time-dependence of the 
Liouvillian or if one wants to solve the master 
equation in the laboratory frame. For example, 
when the transmons have to be excited at 
different frequencies ($\omega_d^1 - \omega_d^2 = 
\delta \neq 0$), from \autoref{eq:RWA} we find 
that even in the doubly-rotating frame, $\hat 
H_{int}$ is oscillating, and it is not possible 
to simply drop this term in RWA because it is 
inherent for the SAM. In this case, to find the 
steady state of the system one can employ the 
qutip's \textit{propagator} and 
\textit{propagator\_steadystate} functions. The 
propagator is a completely positive map 
$\Lambda(t_1, t_0): \hat \rho(t_0) \rightarrow 
\hat \rho(t_1)$ describing the time evolution of 
the system density matrix; for 
\autoref{eq:master}, it is defined as
\begin{equation}
\Lambda(t_1, t_0) = \mathcal{T} \exp [\int_{t_0}^{t_1} \mathcal L(\tau) d\tau],
\label{eq:propagator}
\end{equation}
where $\mathcal T$ is the time-ordering 
superoperator. Since the Liouvillian is periodic 
with a period of $T = 2\pi/\delta$, it is 
possible to calculate the steady state as the 
eigenvector $\hat \rho_{ss}$ of the single-period 
propagator $\Lambda(T, 0)$ corresponding to its 
largest eigenvalue\cite{dittrich1998quantum, 
rivas2012open}. Upon infinitely many applications 
of $\Lambda$
\[
\lim_{n\to \infty} \left[\Lambda(T, 0)\right]^n \hat \rho = \Lambda(nT, 0) \hat \rho \to \hat \rho_{ss}.
\]
